---
title: "Data Wrangling"
runtime: shiny
output:
  html_document:
    css: www/lab.css
    highlight: pygments
    theme: cerulean
    toc: true
    toc_float: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(dplyr)
library(ggplot2)
library(oilabs)
library(pnwflights)
data(flights)
```

Recall from the last lab four elementary data operations:

- `filter()`
- `mutate()`
- `summarize()`
- `group_by()`

This can be strung together in very powerful ways to help reveal the structure in your data.

We're going to use a very similar data set as last lab but shift to a local context. Let's load the packages.

```{r load-packages, message=FALSE}
library(dplyr)
library(ggplot2)
library(oilabs)
library(pnwflights14)
```

The `pnwflights14` package has a data set called `flights` which contains *all* of the flights that left from Seattle-Tacoma International Airport and Portland International Airport in 2014. Let's load that data:

```{r}
data(flights)
```

All of the following exercises require at least a bit of code for their answers.

1.  How many flights left from these two airports in 2014?

2. 


