---
title: "Data Wrangling"
output:
  html_document:
    highlight: pygments
    theme: cerulean
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(dplyr)
library(ggplot2)
library(oilabs)
library(pnwflights14)
data(flights)
```

Recall from the last lab four elementary data operations:

- `filter()`
- `mutate()`
- `summarize()`
- `group_by()`

This can be strung together in very powerful ways to help reveal the structure in your data (`arrange()` might be considered a helpful fifth operation).

We're going to use a very similar data set as last lab but shift to a local context. Let's load the packages.

```{r load-packages, message=FALSE}
library(dplyr)
library(ggplot2)
library(oilabs)
library(pnwflights14)
```

The `pnwflights14` package has a data set called `flights` which contains *all* of the flights that left from Seattle-Tacoma International Airport and Portland International Airport in 2014. Let's load that data:

```{r}
data(flights)
```

All of the following exercises require at least a bit of code for their answers.

1.  How many flights left from these two airports in 2014?

2.  What proportion of these flights left from Portland?

3.  What is the most common destination for flights leaving Portland?

4.  What is the most distant destination from Portland?

5.  Using the airport nearest one of your hometowns, which day of the week and which airline seems best for flying there from Portland? Be clear on how you're defining *best*.

6.  What is the tailnumber of the fastest plane that flew from one of these airports in 2014? Be sure to be clear how you're defining fastest.

